### 2020-07-19 ChapterProblemDefinition/chapterProblemDefinition.tex
Update: Discuss why PhysX is non-deterministic and why this is good

\subsection{Diverging results}\label{divergingResults}
PhysX is non-deterministic, as a result of this, repeating the same scenario with the exact same starting parameters does not necessarily lead to the exact same end state. The order in which collisions are resolved are randomised to achieve greater stability of the simulation.
If collision response is performed on different servers with the same group of objects, they will not lead to the same results. PhysX has an option for increased determinism, but as servers will have different states, as they will be hosting objects that the other server is not, this will not guarantee the exact same results. The results of a single differing collision response can create a significantly different state of objects, for example if a stack of cubes is dropped onto a flat, level plane, the cubes land is such a way where the stack is on the verge of collapsing. In one iteration, the stack of cubes may remain standing, in a second iteration, the stack of cubes may collapse.

>>>>

\subsection{Diverging results}\label{divergingResults}
PhysX is non-deterministic, as a result of this, repeating the same scenario with the exact same starting parameters does not necessarily lead to the exact same end state. The order in which collisions are resolved are randomised to achieve greater stability of the simulation. When there is a queued execution of collision calculations in the collision response phase, the objects considered in the latter stages of the phase are prone to cumulative errors from the previous calculations within the same phase. By randomising the order of the collision calculations each time step, the cumulative error is not propagated into the same objects over multiple time steps.

Due to this non-determinism, if the collision response is performed on different servers with the same group of objects, they will not lead to the same results. PhysX has an option for increased determinism, but as servers will have different states, as they will be hosting objects that the other server is not, this will not guarantee the exact same results. The results of a single differing collision response can create a significantly different state of objects, for example if a stack of cubes is dropped onto a flat, level plane, the cubes land is such a way where the stack is on the verge of collapsing. In one iteration, the stack of cubes may remain standing, in a second iteration, the stack of cubes may collapse.
